HO unification from object language to meta language

### 2024-04-02 paper/main.tex
type in call of printAlll
Update beta sections

In order to guarantee \cref{prop:simulation} we detect
lambdas that can disappear by eta contraction (\cref{sec:etadetection}) and
we modify the term compiler by putting fresh unification variables
in their place: the problematic term is moved from 
from  \hoUnifPb to \linkStore (\cref{sec:etacomp}). The compilation
of the problem \foUnifPb above is refined to: 
%
\printAlll
  {{{\lambda x.X \appsep x,f}}}
  {{{A,f}}}
  {{{X,B,1}}}
  {{{\eta,,A,\lambda x.B_x}}}

@@

\begin{lemma}\label{lem:reduceto}
A $\beta$-normal term $s = \lambda x_1 \ldots x_n.t$
%, where $x, x_1\ldots x_n$ can occur in $t$, 
\reduceto{} $x$ only if one of the following three conditions holds:
\begin{enumerate}
  \item $n = 0$ and $t = x$;
  \item $t$ is the application of $x$ to a list
     of terms $l$ and each $l_i$ \reduceto{} $x_i$
     (e.g. $\lambda x_1 \ldots x_n.x \appsep x_1 \ldots x_n \Eo{} x$) ;
  \item $t$ is a unification variable with scope
    $W$, and for any $v \in \{ x, x_1 \ldots x_n \}$,
    there exists a $w_i \in W$, such that $w_i$ \reduceto{} $v$
    (if $n = 0$ this is equivalent to $x \in W$).
\end{enumerate}
\end{lemma}
\begin{proof}[Proof sketch]
Since our terms are in $\beta$-normal form there is only
one rule that can play a role (namely \ref{clause:eta1}),
hence if the term $s$ is not exactly $x$ (case 1)
it can only be an $\eta$-expansion of it, or a unification
variable that can be assigned to it, or a combination of both.
If $s$ begins with a lambda, then the lambda can only disappear by $\eta$
contraction. In that case the term $t$ under the spine of binders for
$x_1\ldots x_n$ can either be $x$ itself applied to terms that can
\reduceto{} these variables (case 2), or a unification variable
that can be assigned to that application (case 3).
\end{proof}

@@

\newcommand{\testmaybeeta}{\emph{maybe-eta}\xspace}
\begin{definition}[\testmaybeeta]\label{def:testmaybeeta}
  Given a $\beta$-normal term
  $s = \lambda x_1 \ldots x_n.t$, \testmaybeeta{} $s$ holds if any
  of the following holds:
  \begin{enumerate}
    \item $t$ is a constant or variable applied to arguments
      $l_1 \ldots l_m$ such that 
      $m \geq n$ and for every $i$ such that $1 \leq i \leq m-n$
      the term  $l_i$
      \reduceto{} $x_i$, and
      no $x_i$ \occursrigid{} in $l_1 \ldots l_{m-n-1}$;
    \item $t$ is a
      unification variable with scope $W$ and
      for each $x_i$ there exists a $w_j \in W$ such that $w_j$
      \reduceto{} $x_i$.
  \end{enumerate}
\end{definition}
\begin{lemma}[\maybeeta detection]\label{lem:maybeeta}
  If $t$ is a $\beta$-normal term and \testmaybeeta{} $t$ holds,
  then $t \in \maybeeta$.
\end{lemma}
\begin{proof}[Proof sketch]
Follows from \cref{def:occrigid} and \cref{lem:reduceto}
\end{proof}

@@

If we look back the example give at the beginning of this section, we can
deduplicate $\mapping{X}{E}{1}, \mapping{X}{C}{2}$ by removing the first mapping
and adding the auxiliary \linketa: \linketaM{x}{E_{x}}{\lambda y.C_{x y}}.
After deduplication the compiler output is as follows:
% make test ONLY=7001 TEX=tex
\printAlll
  {{{\lambda x.\lambda y.(X\appsep y\appsep x),\lambda x.\lambda y.x},
    {\lambda x.(f\appsep (X\appsep x)\appsep x),Y}}}
  {{{A,\lambda x.\lambda y.x},
    {D,F}}}
  {{{Y,F,0},
    {X,C,2}}}
  {{{x,E_{x},\lambda y.C_{x y}},
    {\eta,,D,\lambda x.(f\appsep E_{x}\appsep x)},
    {\eta,,A,\lambda x.B_{x}},
    {\eta,x,B_{x},\lambda y.C_{y x}}}}
\marginpar{TODO: non so se serva spiegare l'esecuzione (in commento)}
% After unification of the two terms, $X$ is assigned to $\lambda x.\lambda y.x$.
% This assignment makes $l_2$ to progress since the \lhs is materialized and by
% unification, between $X$ and $\lambda x.Y_{x}$, $Y_x$ is instantiate to $\lambda
% y.x$. Once $Y_x$ is instantiated, $l_1$ can progress, and set $H_{xy}$ to $x$.
% After all these progresses, $l_1$ and $l_2$ are remove from \linkStore and the
% \elpiIn{progress} fixpoint terminates. Next, the second unification problem is
% run, and $Z$ is set to $f\appsep(\lambda x.x)$. This unification wakes up $l_3$
% and since $Z$ starts with the \elpiIn{app} node, the $\eta$-expanded version of
% $Z$ is unified with $\lambda x.f \appsep G_{x}~x$ and $G_x$ is set to $x$.
% As last step, the last link is progressed and the final \Ho substitution is
% $\{X _{} \mapsto \lambda x.\lambda y.x, Y _{x} \mapsto \lambda y.x, 
% G _{yx} \mapsto y, Z _{} \mapsto f~\lambda x.x, 
% H _{x} \mapsto \lambda y.y\}$.
% The decompilation phase is only charged, in this example to solve the mappings,
% since no suspended links remain. The only mapping in the list is
% \mapping{F}{H}{2}, which will assign the $F$ variable in \Fo{} to $\lambda xy.y$

@@

It is the case, however, given a list of unification $n$ problems \foUnifPb, if
$\foUnifPb_i$ is in \maybebeta, it is possible that the resolution of the
problems $\bigwedge_{j=0}^{i-1}\foUnifPb_j$ gives a partial substitution
$\rho$, such that $\rho\foUnifPb_i$ falls again in \llambda.
%
\printAlll
  {{{X,\lambda x.Y},
    {(X\appsep a),a}}}
  {{{A,\lambda x.B},
    {(A\appsep a),a}}}
  {{{Y,B,0},
    {X,A,0}}}
  {{}}

In the example above, we see that $\foUnifPb_1$ instantiates $X$ so that
$\foUnifPb_2$, can be solved in \llambda. On the other hand, even though \Uo is
able to solve \foUnifPb, \Ue can't solve the compiled problems \hoUnifPb. In
fact, the resolution of $\hoUnifPb_1$ gives the substitution $\sigma = \{ A
\mapsto \lambda x. B\}$, but the dereferencing of $\hoUnifPb_2$ gives the 
not unifable problem $(\lambda x. B) \appsep a \Ue a$.

In order to encompass this unification, we capture terms $t$ in \maybebeta and
replace them with fresh varaibles $v$. As per \maybebeta, the variables $v$ and
the terms $t$ are linked through a \linkbeta.

\linkbeta guarantee \cref{inv:linklhs} and the term on the \rhs has the
following property:

\begin{invariant}[\linkbeta \rhs]
  The \rhs of any \linkbeta has the shape $X t_1\dots t_n$ such that $X$ is a
  flexible variable and $t_1\dots t_n$ is not in \llambda.
\end{invariant}

@@

\begin{proof}[Proof sketch]
  Given $X \appsep t_1\dots t_n \Ue t$ where $t$ is a rigid term and
  $t_1\dots t_n$ is not in \llambda. By construction, $X \appsep t_1\dots t_n$
  is replaced with a variable $V$, and the \linkbeta \linkbetaM{}{V}{X
  \appsep t_1\dots t_n} is created. The unification instantiates $V$ to $t$,
  making the \lhs of the link a rigid term, while \rhs is still in \maybebeta.
  The original problem is in fact outside \llambda and unification fails.
\end{proof}

@@

The list \elpiIn{Ag} is split into the list \elpiIn{Pf} and \elpiIn{Extra} such
that \elpiIn{append Pf Extra Ag} and \elpiIn{Pf} is the largest prefix of
\elpiIn{Ag} such that \elpiIn{Pf} is in \llambda. The \rhs of the \linkbeta is
the application of a fresh variable \elpiIn{C} having in scope all the compiled
list of terms obtained from \elpiIn{Pf} and \elpiIn{Extra1} as arguments. The
variable \elpiIn{B} returned has compiled terms is a fresh variable having in
scope all the free variables used in \rhs.

\begin{invariant}
  The \rhs of a \linkbeta has the shape \elpiIn{app[uva N S|L]}.
\end{invariant}

@@

\begin{proof}[Proof sketch]
  By contradiction, if \elpiIn{L} is a empty list, then the original \Fo{}
  term has the shape \elpiIn{fapp[fuva M | Ag]} where \elpiIn{Ag} is a list of 
  disting names. This case is however captured by rule~\ref{rule:complam} (from
  \cref{sec:compilation}) and no \linkbeta is produced: a contradiction.
\end{proof}

\begin{corollary}
  Let \elpiIn{app[uva N S|L]} be the \rhs of a \linkbeta, then the 
  first argument $t$ in \elpiIn{L} either appears in \elpiIn{S} or it is 
  not a name.
\end{corollary}

@@

Once created, there exist two main situations waking up a suspended \linkbeta.
The former is strictly connected to the definition of $\beta$-redex and occurs
when the head of \rhs is materialized by the oracle (see
\cref{prop:simulation}). In this case \rhs is safely\marginpar{explain why}
$\beta$-reduced to a new term $t'$ and the result can be unified with \lhs. In
this scenario the \linkbeta has accomplished its goal and can be removed from
\linkStore.

The second circumstance making the \linkbeta to progress is the instantiation of
the variables in the \elpiIn{Extra1} making the corresponding arguments to
reduce to names. In this case, we want to take the list \elpiIn{Scope1} and
append to it the largest prefix of \elpiIn{Extra1} in a new variable
\elpiIn{Scope2} such that \elpiIn{Scope2} remains in \llambda; we call
\elpiIn{Extra2} the suffix of \elpiIn{Extra1} such that the concatenation of
\elpiIn{Scope1} and \elpiIn{Extra1} is the same as the concatenation of
\elpiIn{Scope2} and \elpiIn{Extra2}. Finally, two cases should be considered: 1)
\elpiIn{Extra2} is the empty list, \lhs and rhs can be unified: we have two
terms in \llambda; otherwise 2) the \linkbeta in question is replaced with a
refined version where the \rhs is  \elpiIn{app[uva C Scope2 | Extra2]} and a new
\linketa is added between the \lhs and the new-added variable \elpiIn{C}.
\marginpar{dire che si adatta bene nelle approximation}

An example justifying this second  link manipulation is given by the following
unification problem:

\def\varF{\ensuremath{\textbf{F}}\xspace}
\def\varA{\ensuremath{\textbf{A}}\xspace}
\def\varB{\ensuremath{\textbf{B}}\xspace}

\begin{elpicode}
  f = flam x\ fapp[F, fapp[A, x]].
\end{elpicode}

% \begin{elpicode};
%   f = flam x\ flam y\ fapp[F, fapp[A, x], fapp[B, y]].
% \end{elpicode}

The compilation of these terms produces the new unification problem: $f = X0$

We obtain the mappings $\mapping{F}{\varF}{0}, \mapping{A}{\varA}{1}$ and the links:
%
\begin{gather}
  \linkbetaM{c0}{X3_{c0}}{X2~X1_{c0}}\\
  \linketaM{}{X0}{\lambda c0.X3_{c0}}
\end{gather}

\noindent
where the first link is a \linketa between the variable \texttt{X0}, representing
the right side of the unification problem (it is a \maybeeta) and
\texttt{X3}; and a \linkbeta between the variable \texttt{X3} and the subterm
$\lambda x.X1_x ~ a$ (it is a \maybebeta).
The substitution tells that \substCell{x}{X1_x}{x}.

We can now represent the \hrun execution from this configuration which will, at
first, dereference all the links, and then try to solve them. The only link
being modified is the second one, which is set to \linkbetaM{x}{X3}{X2 x a}. The
\rhs of the link has now a variable which is partially in the PF, we can
therefore remove the original \linkbeta and replace it with the following couple
on links:

\begin{textcode}
  ~$\vdash$~ X1   =~$\eta$~= x\ `X4 x'
x ~$\vdash$~ X3 x =~$\beta$~= x\ `X4 x' a
\end{textcode}

By these links we say that \texttt{X1} is now $\eta$-linked to a fresh variable
\texttt{X4} with arity one. This new variable is used in the new \linkbeta where
the name \texttt{x} is in its scope. This allows

>>>>

In order to guarantee \cref{prop:simulation} we detect
lambdas that can disappear by eta contraction (\cref{sec:etadetection}) and
we modify the compiled terms by putting fresh unification variables
in their place: the problematic term is moved 
from  \hoUnifPb to \linkStore (\cref{sec:etacomp}). The compilation
of the problem \foUnifPb above is refined to: 
%
\printAlll
  {{{\lambda x.X \appsep x,f}}}
  {{{A,f}}}
  {{{X,B,1}}}
  {{{\eta,,A,\lambda x.B_x}}}

@@

\begin{lemma}\label{lem:reduceto}
A $\beta$-normal term $s = \lambda x_1 \ldots x_n.t$
%, where $x, x_1\ldots x_n$ can occur in $t$, 
\reduceto{} $x$ only if one of the following three conditions holds:
\begin{enumerate}
  \item $n = 0$ and $t = x$;
  \item $t$ is the application of $x$ to a list
     of terms $l$ and each $l_i$ \reduceto{} $x_i$
     (e.g. $\lambda x_1 \ldots x_n.x \appsep x_1 \ldots x_n \Eo{} x$) ;
  \item $t$ is a unification variable with scope
    $W$, and for any $v \in \{ x, x_1 \ldots x_n \}$,
    there exists a $w_i \in W$, such that $w_i$ \reduceto{} $v$
    (if $n = 0$ this is equivalent to $x \in W$).
\end{enumerate}
\end{lemma}
\begin{proof}[Proof sketch]
Since our terms are in $\beta$-normal form there is only
one rule that can play a role (namely \ref{clause:eta1}),
hence if the term $s$ is not exactly $x$ (case 1)
it can only be an $\eta$-expansion of $x$, or a unification
variable that can be assigned to $x$, or a combination of both.
If $s$ begins with a lambda, then the lambda can only disappear by $\eta$
contraction. In that case the term $t$ under the spine of binders for
$x_1\ldots x_n$ can either be $x$ itself applied to terms that can
\reduceto{} these variables (case 2), or a unification variable
that can be assigned to that application (case 3).
\end{proof}

@@

\newcommand{\testmaybeeta}{\emph{maybe-eta}\xspace}
\begin{definition}[\testmaybeeta]\label{def:testmaybeeta}
  Given a $\beta$-normal term
  $s = \lambda x_1 \ldots x_n.t$, \testmaybeeta{} $s$ holds if any
  of the following holds:
  \begin{enumerate}
    \item $t$ is a constant or a variable applied to the arguments
      $l_1 \ldots l_m$ such that 
      $m \geq n$ and for every $i$ such that $1 \leq i \leq m-n$
      the term  $l_i$
      \reduceto{} $x_i$, and
      no $x_i$ \occursrigid{} in $l_1 \ldots l_{m-n-1}$;
    \item $t$ is a
      unification variable with scope $W$ and
      for each $x_i$ there exists a $w_j \in W$ such that $w_j$
      \reduceto{} $x_i$.
  \end{enumerate}
\end{definition}
\begin{lemma}[\maybeeta detection]\label{lem:maybeeta}
  If $t$ is a $\beta$-normal term and \testmaybeeta{} $t$ holds,
  then $t \in \maybeeta$.
\end{lemma}
\begin{proof}[Proof sketch]
Follows from \cref{def:occrigid} and \cref{lem:reduceto}
\end{proof}

@@

If we look back the example give at the beginning of this section, we can
deduplicate $\mapping{X}{E}{1}, \mapping{X}{C}{2}$ by removing the first mapping
and adding the auxiliary \linketa: \linketaM{x}{E_{x}}{\lambda y.C_{x y}}.
After deduplication the compiler output is as follows:
% make test ONLY=7001 TEX=tex
\printAlll
  {{{\lambda x.\lambda y.(X\appsep y\appsep x),\lambda x.\lambda y.x},
    {\lambda x.(f\appsep (X\appsep x)\appsep x),Y}}}
  {{{A,\lambda x.\lambda y.x},
    {D,F}}}
  {{{Y,F,0},
    {X,C,2}}}
  {{{\eta,x,E_{x},\lambda y.C_{x y}},
    {\eta,,D,\lambda x.(f\appsep E_{x}\appsep x)},
    {\eta,,A,\lambda x.B_{x}},
    {\eta,x,B_{x},\lambda y.C_{y x}}}}
\marginpar{TODO: non so se serva spiegare l'esecuzione (in commento)}
% After unification of the two terms, $X$ is assigned to $\lambda x.\lambda y.x$.
% This assignment makes $l_2$ to progress since the \lhs is materialized and by
% unification, between $X$ and $\lambda x.Y_{x}$, $Y_x$ is instantiate to $\lambda
% y.x$. Once $Y_x$ is instantiated, $l_1$ can progress, and set $H_{xy}$ to $x$.
% After all these progresses, $l_1$ and $l_2$ are remove from \linkStore and the
% \elpiIn{progress} fixpoint terminates. Next, the second unification problem is
% run, and $Z$ is set to $f\appsep(\lambda x.x)$. This unification wakes up $l_3$
% and since $Z$ starts with the \elpiIn{app} node, the $\eta$-expanded version of
% $Z$ is unified with $\lambda x.f \appsep G_{x}~x$ and $G_x$ is set to $x$.
% As last step, the last link is progressed and the final \Ho substitution is
% $\{X _{} \mapsto \lambda x.\lambda y.x, Y _{x} \mapsto \lambda y.x, 
% G _{yx} \mapsto y, Z _{} \mapsto f~\lambda x.x, 
% H _{x} \mapsto \lambda y.y\}$.
% The decompilation phase is only charged, in this example to solve the mappings,
% since no suspended links remain. The only mapping in the list is
% \mapping{F}{H}{2}, which will assign the $F$ variable in \Fo{} to $\lambda xy.y$

@@

It is the case, however, given a list of unification $n$ problems \foUnifPb, if
$\foUnifPb_i$ is in \maybebeta, it is possible that the resolution of the
problems $\bigwedge_{j=0}^{i-1}\foUnifPb_j$ gives a partial substitution
$\rho$, such that $\rho\foUnifPb_i$ falls again in \llambda.
%
% make test ONLY=7003 TEX=TEX + deactivate beta tex
\printAlll
  {{{X,\lambda x.Y},
    {(X\appsep a),a}}}
  {{{A,\lambda x.B},
    {(A\appsep a),a}}}
  {{{Y,B,0},
    {X,A,0}}}
  {{}}

In the example above, we see that $\foUnifPb_1$ instantiates $X$ so that
$\foUnifPb_2$, can be solved in \llambda. On the other hand, we see that, 
\Ue can't solve the compiled problems \hoUnifPb. In
fact, the resolution of $\hoUnifPb_1$ gives the substitution $\sigma = \{ A
\mapsto \lambda x. B\}$, but the dereferencing of $\hoUnifPb_2$ gives the 
non-unifable problem $(\lambda x. B) \appsep a \Ue a$.

In order to encompass this unification, term compilation should capture the
terms $t$ in \maybebeta and replace them with fresh varaibles $v$. As per
\maybebeta, the variables $v$ and the terms $t$ are linked through a \linkbeta.

\linkbeta guarantees \cref{inv:linklhs} and the term on the \rhs has the
following property:

\begin{invariant}[\linkbeta \rhs]
  The \rhs of any \linkbeta has the shape $X~t_1\dots t_n$ such that $X$ is a
  flexible variable and $t_1\dots t_n$ is not in \llambda.
\end{invariant}

@@

\begin{proof}[Proof sketch]
  Given $X \appsep t_1\dots t_n \Ue t$ where $t$ is a rigid term and
  $t_1\dots t_n$ is not in \llambda. By construction, $X \appsep t_1\dots t_n$
  is replaced with a variable $V$, and the \linkbeta \linkbetaM{\Gamma}{V}{X
  \appsep t_1\dots t_n} is created. The unification instantiates $V$ to $t$,
  making the \lhs of the link a rigid term, while \rhs is still in \maybebeta.
  The original problem is in fact outside \llambda and unification fails.
\end{proof}

@@

The list \elpiIn{Ag} is split into the list \elpiIn{Pf} and \elpiIn{Extra} such
that \elpiIn{append Pf Extra Ag} and \elpiIn{Pf} is the largest prefix of
\elpiIn{Ag} such that \elpiIn{Pf} is in \llambda. The \rhs of the \linkbeta is
the application of a fresh variable \elpiIn{C} having in scope all the free
variables appearing in the compiled version of \elpiIn{Pf} and \elpiIn{Extra}. The
variable \elpiIn{B}, returned has the compiled term, is a fresh variable having in
scope all the free variables occurring in \elpiIn{Pf1}.

\newcommand{\rhsBeta}{\ensuremath{N_S\appsep L}\xspace}

\begin{invariant}
  The \rhs of a \linkbeta has the shape \rhsBeta (equivalent to
  \elpiIn{app[uva N S|L]}).
\end{invariant}

@@

\begin{proof}[Proof sketch]
  By contradiction, if \elpiIn{L} is a empty list, then the original \Fo{} term
  has the shape \elpiIn{fapp[fuva M | Ag]} where \elpiIn{Ag} is a list of
  distinct names (i.e. there list \elpiIn{Extra} is empty). This case is however
  captured by rule~\ref{rule:complam} (from \cref{sec:compilation}) and no
  \linkbeta is produced: a contradiction.
\end{proof}

\begin{corollary}
  Let \rhsBeta be the \rhs of a \linkbeta, then the 
  first argument $t$ in \elpiIn{L} either appears in \elpiIn{S} or it is 
  not a name.
\end{corollary}

@@

\newcommand{\progBetaLL}{progress-beta-llambda}
\newcommand{\progBetaRH}{progress-beta-rigid-head}

The activation of a \linkbeta is performed when its \rhs falls under \llambda
under a given substitution.

\begin{definition}[\progBetaLL]
  A link \linkbetaM{\Gamma}{X}{N_S\appsep [t|L]} is removed from \linkStore, if
  it exists a substitution $\gamma$, such that the first term $t$ is a name no
  occurring in $S$. In this case, let $M$ a fresh variable, then the new links
  \linkbetaM{\Gamma,x}{X}{M_{S,n}\appsep L} and \linketaM{\Gamma}{N}{\lambda
  x.M_x} are added to \linkStore.
\end{definition}

\begin{definition}[\progBetaRH]
  A link \linkbetaM{\Gamma}{X}{\rhsBeta} is removed from
  \linkStore if $N_S$ is instantiated to a term $t$ and the
  $\beta$-reduced term $t'$ obtained from the application of $t$ to
  $L$ is in \llambda. Moreover, $X$ is unified to $t$.
\end{definition}

\begin{lemma}
  \elpiIn{progress} terminates
\end{lemma}

\begin{proof}[Proof sketch]
  TODO: bla
\end{proof}

\begin{corollary}
  Given \linkbetaM{\Gamma}{X}{\rhsBeta}, then \elpiIn{distinct-name} $S$ holds.  
\end{corollary}

\paragraph{Example of \progBetaLL} 
A simple example of \linkbeta progression due to \progBetaLL is given below:

% make test ONLY=7004 TEX=tex
\printAlll
  {{{X,\lambda x.x},
    {\lambda x.(Y\appsep (X\appsep x)),a}}}
  {{{A,\lambda x.x},
    {B,a}}}
  {{{Y,D,0},
    {X,A,0}}}
  {{{\eta,,A,\lambda x.E_{x}},
    {\eta,,B,\lambda x.C_{x}},
    {\beta,x,C_{x},(D\appsep E_{x})}}}

The \linkbeta in \linkStore has a variable $D$ applied to the variable $E_x$.
The first unification problem, $\hoUnifPb_1$ produces the substitution $\sigma =
\{A \mapsto \lambda x.x\}$. This instantiation triggers $\linkStore_1$ which
before its removal, assignes $E$ to $\lambda x.x$. Now, the \linkbeta is
\linkbetaM{x}{C_x}{(D \appsep x)}. This link is replaced with the couple of
links: \linkbetaM{x}{C_x}{F_x}, \linketaM{}{E}{\lambda x.D_x}. $\hoUnifPb_2$
assignes $B$ which activates $\linkStore_2$, and then all the remaining links
are solved. The final \Ho substitution is $\sigma = \{A = \lambda x.x, B = a,
C_x = a, D = \lambda \}$ and is decompiled into $\rho = \{X \mapsto \lambda x.x,
Y \mapsto a\}$.

\paragraph{Example of \progBetaRH}
We can take the example provided in \cref{sec:beta}. The problem is compiled
into:
%
% make test ONLY=7003 TEX=tex
\printAlll
  {{{X,\lambda x.Y},
    {(X\appsep a),a}}}
  {{{A,\lambda x.B},
    {C,a}}}
  {{{Y,B,0},
    {X,A,0}}}
  {{{\beta,,C,(A\appsep a)}}}

The first unification, $\hoUnifPb_1$, gives the substitution $\sigma = \{A
\mapsto \lambda x.B\}$. The \linkbeta, $\linkStore_1$, becomes
\linkbetaM{}{C}{((\lambda x.B) \appsep a)} whose \rhs can be $\beta$-reduced to
$B$. $B$ is in \llambda and is unified with $C$. The resolution of $\hoUnifPb_2$
gives the final substitution $\sigma = \{A \mapsto \lambda x.B, B \mapsto C, C
\mapsto a\}$ which is decompiled into $\rho = \{X \mapsto \lambda x.a, Y \mapsto
a\}$.
